Inference of Gravitational Lens Time Delays Using Gaussian Processes

### 2013-04-21 doc/Leon/ms.tex
A table

Suppose that the underlying QSO variability as a function of time is
described by:
\begin{eqnarray}
y_{\rm QSO}(t)
\end{eqnarray}
Then the light curves of the two images $A$ and $B$ will be given by:
\begin{eqnarray}
y_A(t) &=& y_{\rm QSO}(t) + \mu_A(t)\\
y_B(t) &=& y_{\rm QSO}(t - \tau) + \mu_B(t)
\end{eqnarray}
where $\mu_A(t)$ and $\mu_B(t)$ are microlensing perturbations.

@@

The probability distribution for the data $\yy$ given the parameters
$\theta$
is a multivariate normal distribution, where the mean vector $\mm$
and the covariance matrix $\CC$ depend on the parameters:
\begin{eqnarray}
p(\yy | \theta) &=& \frac{1}{\sqrt{(2\pi)^N\det{\CC}}}
\exp\left[
-\frac{1}{2}
\left(
\yy - \mm
\right)^T
\CC^{-1}
\left(
\yy - \mm
\right)
\right]
\end{eqnarray}

Numerically, the logarithm of the determinant and the
$\CC^{-1}\left(\yy - \mm\right)$ term are implemented using
Cholesky decompositions.

>>>>

Suppose that the underlying QSO variability as a function of time is
described by:
\begin{eqnarray}
y_{\rm QSO}(t)
\end{eqnarray}
Then the light curves of the two images $A$ and $B$ will be given by:
\begin{eqnarray}
y_A(t) &=& y_{\rm QSO}(t) + \mu_A(t)\\
y_B(t) &=& y_{\rm QSO}(t - \tau) + \mu_B(t)
\end{eqnarray}
where $\mu_A(t)$ and $\mu_B(t)$ are perturbations due to microlensing.

@@

The probability distribution for the data $\yy$ given the parameters
$\theta$
is a multivariate normal distribution, where the mean vector $\mm$
and the covariance matrix $\CC$ depend on the parameters:
\begin{eqnarray}
p(\yy | \theta) &=& \frac{1}{\sqrt{(2\pi)^N\det{\CC}}}
\exp\left[
-\frac{1}{2}
\left(
\yy - \mm
\right)^T
\CC^{-1}
\left(
\yy - \mm
\right)
\right]
\end{eqnarray}
Numerically, the logarithm of the determinant and the
$\CC^{-1}\left(\yy - \mm\right)$ term are implemented using
Cholesky decompositions.

\begin{table}[h!]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Parameter & Description & Prior\\
\hline
$\{m_k\}$ & Mean magnitudes for each image & Uniform$(m_{\rm min}, m_{\rm max})$\\
$\{\tau_k\}$ & Time delays for each image & Cauchy$(0, \tau_{\rm range}/10)T(\tau_{\rm min}, \tau_{\rm max})$\\
\end{tabular}
\end{center}
\end{table}
